White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2016-06-28 documentation/userguide.tex
Update bibliography file reference in the documentation

Decide what directory you want to build the problem in. It is expected 
to be a subdirectory of the \texttt{results/} directory, which will be
automatically created for you:
\begin{lstlisting}
dir=results/test_problem/
\end{lstlisting}
Now, optionally decide how many processors you want to run with, and 
how long you want the job to run:
\begin{lstlisting}
nprocs=128
walltime=4:00:00
\end{lstlisting}
If you do not, the job submission script will default to running the job
using one node for one hour. Finally, run your job:
\begin{lstlisting}
run $dir $nprocs $walltime
\end{lstlisting}%$
That is all you need to submit a job. Return to the terminal, and type \texttt{bash run.sh}
and your job will execute. The helper function \texttt{run} does several things. First, 
it creates the directory named \texttt{\$dir}. Then, it copies into \texttt{\$dir} the \texttt{inputs}
and \texttt{probin} files from the root \texttt{wdmerger} source directory; these are the runtime
files \texttt{CASTRO} needs to determine what your problem setup will be. They contain the default 
parameters for merger runs. It also copies any auxiliary files one might need, like the 
table for the equation of state, as well as the actual \texttt{CASTRO} executable you just built in the 
\texttt{compile/} directory. Finally, it builds a script that you'll use for actually submitting 
the job to the batch submission system on the machine you're on, and then submits that job. 
Thus for a typical setup, your run directory will contain the following files when you submit:
\begin{itemize}
  \item \texttt{Castro3d*.ex}
  \item \texttt{helm\_table.dat}
  \item \texttt{inputs}
  \item \texttt{probin}
  \item \texttt{run\_script}
\end{itemize}
Typically you'll want to run multiple jobs at once, that vary things like the number of processors 
or the runtime parameters. For example, suppose we want to run the same problem but we want to 
explore what happens when we change the rotational period of the system. The main helper functions 
will automatically handle this for you as long as your variable is part of a valid namespace in the inputs files.
The orbital period is handled by the inputs parameter \texttt{castro.rotational\_period}. Therefore 
we simply need to update a variable named \texttt{castro\_rotational\_period}. 
Note that we use an underscore (\texttt{castro\_}) and not a period (\texttt{castro.}) after the namespace.
This is simply because \texttt{bash} does not permit periods in variable names; but the helper routine will 
automatically take care of this for you when looking for the appropriate variable in the inputs file.
A sample script follows:

@@

\bibliographystyle{../papers/apj}
\bibliography{../papers/refs}

>>>>

Decide what directory you want to build the problem in. It is expected 
to be a subdirectory of the \texttt{results/} directory, which will be
automatically created for you:
\begin{lstlisting}
dir=results/test_problem/
\end{lstlisting}
Now, optionally decide how many processors you want to run with, and 
how long you want the job to run:
\begin{lstlisting}
nprocs=128
walltime=4:00:00
\end{lstlisting}
If you do not, the job submission script will default to running the job
using one node for one hour. Finally, run your job:
\begin{lstlisting}
run $dir $nprocs $walltime
\end{lstlisting}%$
That is all you need to submit a job. Return to the terminal, and type \texttt{bash run.sh}
and your job will execute. The helper function \texttt{run} does several things. First, 
it creates the directory named \texttt{\$dir}. Then, it copies into \texttt{\$dir} the \texttt{inputs}
and \texttt{probin} files from the root \texttt{wdmerger} source directory; these are the runtime
files \texttt{CASTRO} needs to determine what your problem setup will be. They contain the default 
parameters for merger runs. It also copies any auxiliary files one might need, like the 
table for the equation of state, as well as the actual \texttt{CASTRO} executable you just built in the 
\texttt{compile/} directory, and a copy of the run utilities that manage the job itself (so that the 
run doesn't change if you make local edits to the job management system). Finally, it builds a script 
that you'll use for actually submitting the job to the batch submission system on the machine you're on, 
and then submits that job. Thus for a typical setup, your run directory will contain at least the following 
files when you submit:
\begin{itemize}
  \item \texttt{Castro3d*.ex}
  \item \texttt{helm\_table.dat}
  \item \texttt{inputs}
  \item \texttt{probin}
  \item \texttt{run\_script}
  \item \texttt{job\_scripts/}
\end{itemize}
Note that if you want to set up this directory as above but \textit{not} actually submit the job, 
set the \texttt{no\_submit} variable to any value in your run script. Similarly, if you want to 
set up the directory to contain the inputs and probin file but none of the machine-dependent 
scripts or the executable, set the \texttt{inputs\_only} variable to any value in your run script.

Typically you'll want to run multiple jobs at once, that vary things like the number of processors 
or the runtime parameters. For example, suppose we want to run the same problem but we want to 
explore what happens when we change the rotational period of the system. The main helper functions 
will automatically handle this for you as long as your variable is part of a valid namespace in the inputs files.
The orbital period is handled by the inputs parameter \texttt{castro.rotational\_period}. Therefore 
we simply need to update a variable named \texttt{castro\_rotational\_period}. 
Note that we use an underscore (\texttt{castro\_}) and not a period (\texttt{castro.}) after the namespace.
This is simply because \texttt{bash} does not permit periods in variable names; but the helper routine will 
automatically take care of this for you when looking for the appropriate variable in the inputs file.
A sample script follows:

@@

\bibliographystyle{../papers/aasjournal}
\bibliography{../papers/refs}

### 2016-06-28 papers/wdmerger_II/paper.tex

>>>>

The simulation is terminated when the total energy is positive, indicating that
the system has become unbound due to nuclear energy release, and has been
constant or decreasing for the last five timesteps, indicating that no further
meaningful nuclear energy generation is occurring and material is now beginning
to stream off the simulation domain. As all simulations in this paper are of
WD collisions that generate enough energy to unbind the system, this stopping
criterion is applied throughout all simulations shown here.
